\clearpage

The logic programming approach to computing investigates the use of logic as a programing language
and explores computational models based on controlled deduction.

\ru{Подход логического программирования к вычислениям исследует использование логики 
в качестве языка программирования и исследует вычислительные модели, основанные на управляемом выводе.}

The field of logic programming has seen a tremendous growth in the last several years, 
both in depth and in scope. This grows is reflected in the number of articles, journals, 
these, books, workshops, and conferences devoted to the subject. 
The MIT Press series in logic programming was created to accommodate this development 
and to nurture it. It is dedicated to the publication of high-quality textbooks, 
monographs, collections, and proceedings in logic program\-ming.

\ru{За последние несколько лет область логического программирования значительно 
расширилась как по глубине, так и по объему. Этот рост отражается в количестве статей, 
журналов, книг, семинаров и конференций, посвященных этой теме. 
Серия MIT Press по логическому программированию была создана для того, чтобы 
приспособиться к этому развитию и развивать его. Он посвящен публикации высококачественных 
учебников, монографий, и сборников по логическому программированию.}

\bigskip

\noindent\copyright\ \cite{taop}\ Ehud Shapiro\\ The Weizmann Institute of Science\\Rehovot, Israel

\bigskip

Programming in \pro\ opens the mind to a new way of looking at compu\-ting.
There is a change of perspective that every \pro\ programmer experiences when first getting to know the language.

\ru{Программирование на \pro\ открывает разум для нового взгляда на вычисления.
Существует изменение перспективы, с которой сталкивается каждый \pro-программист, когда впервые знакомится с языком.}

